Mermaid with R + consort

### 2023-07-05 Analysis/data_organize.qmd
started new analysis + re-render

```{r}
pacman::p_load(tidyverse,lme4,emmeans,here)
d <- readRDS(here("data/dPrune-05-21-23.rds"))
d$stage <- factor(d$stage, levels = c("1","2","3","4","5","6","7","8","9","10","11","12","13","14","15","16","17","18","19","20","21","22","23"))
d$tOrder <- factor(d$tOrder, levels=c("testFirst","trainFirst"))

@@

```{r}
head(d)
colnames(d)

# identify which columns are factors
d %>% select_if(is.factor) %>% colnames()

# show levels of each factor variable
d %>% select_if(is.factor) %>% map(levels)

```{r}

>>>>

```{r}
pacman::p_load(tidyverse,lme4,emmeans,here,knitr,kableExtra)
options(dplyr.summarise.inform=FALSE)
d <- readRDS(here("data/dPrune-05-21-23.rds")) %>% ungroup()
d$stage <- factor(d$stage, ordered=TRUE, levels = c("1","2","3","4","5","6","7","8","9","10","11","12","13","14","15","16","17","18","19","20","21","22","23"))
d$tOrder <- factor(d$tOrder, levels=c("testFirst","trainFirst"),labels=c("Test First","Train First"))
d$bandOrder <- factor(d$catOrder,levels=c("orig","rev"),labels=c("Original","Reverse"))
d$fb <- factor(d$fb,levels=c("Continuous","Ordinal"),labels=c("Continuous","Ordinal"))
d<- d %>% mutate(id=as.factor(d$id),fullCond=as.factor(fullCond)) %>% select(-catOrder,-mode) %>% relocate(bandOrder,.after=fb)
```

head(d)
colnames(d)
d %>% select_if(is.factor) %>% colnames()

```{r}
d %>% select_if(is.factor) %>% select(-sbjCode,-id) %>% map(levels)
```

```{r}
#| eval: false
e1 <- d |> filter(fb=="Continuous" & bandOrder=="Original")
e2 <- d |> filter(fb=="Continuous" & bandOrder=="Reverse")
e3 <- d |> filter(fb=="Ordinal")

saveRDS(d,here("data/dAll_07_04_23.rds"))
saveRDS(e1,here("data/e1_07_04_23.rds"))
saveRDS(e2,here("data/e2_07_04_23.rds"))
saveRDS(e3,here("data/e3_07_04_23.rds"))

@@

### 2023-07-05 Visuals_Interactives/mermaid_consort.qmd
started new analysis + re-render

# Generate the mermaid diagram
makemermaid(x,
            I1 = '![Gaussian Curve](gaussian_curve_input_node_1.png)',
            I2 = '![Gaussian Curve](gaussian_curve_input_node_2.png)',
            I3 = '![Gaussian Curve](gaussian_curve_input_node_3.png)',
            file = 'alm_exam.mer'
            )

# Output the mermaid diagram
# cat('```{mermaid}\n')
# cat(readLines('alm_exam.mer'), sep = '\n')
# cat('```\n')

@@

```{mermaid}
%%| fig-cap: "ALM diagram produced with `mermaid` with individual exclusions linked to the overall exclusions node, and with a tooltip to show more detail"
%%| label: fig-doverview-mermaid2
%%| file: alm_exam.mer
```

@@

w <- r[, 
makemermaid(x,
            N0   = nrow(r),
            excl = htab(exc, 'Excluded', br='<br>'),
            Nq   = count(is.na(exc)),
            Nc   = count(consent),
            Nr   = count(randomized),
            Ntxa = count(tx == 'A'),
            Ntxb = count(tx == 'B'),
            Ntxaf= count(tx == 'A' & fin),
            Ntxbf= count(tx == 'B' & fin),
            Ntxao= count(tx == 'A' & ! is.na(y)),
            Ntxbo= count(tx == 'B' & ! is.na(y)),
            file = 'mermaid1.mer'
            )
]

@@

```{mermaid}
%%| fig-cap: "Consort diagram produced by `mermaid`"
%%| label: fig-doverview-mermaid1
%%| file: mermaid1.mer
```

@@

```{mermaid}
%%| fig-cap: "Consort diagram produced with `mermaid` with individual exclusions linked to the overall exclusions node, and with a tooltip to show more detail"
%%| label: fig-doverview-mermaid2
%%| file: mermaid2.mer
```

>>>>

# Generate the mermaid diagram
makemermaid(x,
            I1 = '![Gaussian Curve](gaussian_curve_input_node_1.png)',
            I2 = '![Gaussian Curve](gaussian_curve_input_node_2.png)',
            I3 = '![Gaussian Curve](gaussian_curve_input_node_3.png)',
            file = 'assets/alm_exam.mer'
            )

# Output the mermaid diagram
# cat('```{mermaid}\n')
# cat(readLines('assets/alm_exam.mer'), sep = '\n')
# cat('```\n')

@@

```{mermaid}
%%| fig-cap: "ALM diagram produced with `mermaid` with individual exclusions linked to the overall exclusions node, and with a tooltip to show more detail"
%%| label: fig-doverview-mermaid2
%%| file: assets/alm_exam.mer
```

@@

w <- r[, 
makemermaid(x,
            N0   = nrow(r),
            excl = htab(exc, 'Excluded', br='<br>'),
            Nq   = count(is.na(exc)),
            Nc   = count(consent),
            Nr   = count(randomized),
            Ntxa = count(tx == 'A'),
            Ntxb = count(tx == 'B'),
            Ntxaf= count(tx == 'A' & fin),
            Ntxbf= count(tx == 'B' & fin),
            Ntxao= count(tx == 'A' & ! is.na(y)),
            Ntxbo= count(tx == 'B' & ! is.na(y)),
            file = 'assets/mermaid1.mer'
            )
]

@@

```{mermaid}
%%| fig-cap: "Consort diagram produced by `mermaid`"
%%| label: fig-doverview-mermaid1
%%| file: assets/mermaid1.mer
```

@@

```{mermaid}
%%| fig-cap: "Consort diagram produced with `mermaid` with individual exclusions linked to the overall exclusions node, and with a tooltip to show more detail"
%%| label: fig-doverview-mermaid2
%%| file: assets/mermaid2.mer
```
